DATA 624 Homework 4

### 2020-02-26 DATA624/HW4.Rmd
Minor change

```{r setup, echo=FALSE, cache=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(tidyverse)
library(fpp2)
library(forecast)
library(readxl)
library(seasonal)
```

@@

(a) Investigate the frequency distributions for the categhorical predictors.  Are any of the distributions degenerate in the ways discussed earlier in this chapter?

>>>>

```{r setup, echo=FALSE, cache=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(tidyverse)
```

@@

(a) Investigate the frequency distributions for the categorical predictors.  Are any of the distributions degenerate in the ways discussed earlier in this chapter?
